Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-18 ms.qmd
Starting more detailed map

>>>>

zoom_areas <- data.frame(
     x = c(-130,  -10, 130),
     y = c(  25, 30, -25),
  xend = c( -50, 45, 170),
  yend = c(  55,  70, -5),
  label = c("North America", "Europe", "Asia")
)

zoom_plots <- lapply(1:nrow(zoom_areas), function(i) {
  map1_current +
    geom_polygon(fill = "gray80", color = "black") +
    coord_cartesian(xlim = c(zoom_areas[i, "x"], zoom_areas[i, "xend"]), 
                    ylim = c(zoom_areas[i, "y"], zoom_areas[i, "yend"])) +
                    theme(legend.position = "none")
})

p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])
